ZCB Pricing

### 2018-08-07 Draft.tex
Update Draft.tex
kjkh

	\begin{center}
		\textbf{{\Large Draft Paper}}\\
		\vspace{1cm}
		{\Large Pricing a zero coupon bond by Monte Carlo and Finite Difference Methods when the term structure of interest rates is a mean reverting Ornstein-Uhlenbeck process}\\
		\vspace{1cm}
		\today\\
		Valentine Chisango (CHSVAL002)\\
		{\tt vmchisango@gmail.com}\\

@@

\begin{abstract}
	This paper examines the methods used to price a zero coupon bonds under the Ornstein Uhenbleck process. This paper considers the use Monte Carlo simulations together with various variance reduction techniques to verify improvments in stability of estimates. The simulation method is compared to various finitie difference techniques to analyse the difference in convergence and speed in evaluating solutions.The various methods are compared to the closed form solution to assess the accuracy. 
\end{abstract}

@@

\section{Introduction}
The pricing of securities is a critical task that many financial institutions must complete. In some instances, these securities have simple enough pricing equations with closed form solutions and so they can be solved analytically. A zero-coupon bond is an example of such an instrument. However, in many cases the closed form solution is not known and a numerical approach is necessary. Most options fall into this category. As such, it is valuable to know which numerical method performs the best and should therefore be used for such cases. Fortunately, the analytical solution for a zero coupon bond can be used to compare the quality of results produced by numerical methods to price the same security and thus draw some conclusions about the performance of these methods for general use. 
\label{sec: Intro}

>>>>

	\begin{center}
		\textbf{{\Large Draft Paper}}\\
		\vspace{1cm}
		{\Large Pricing a zero-coupon bond by Monte Carlo and Finite Difference Methods when the term structure of interest rates is a mean reverting Ornstein-Uhlenbeck process}\\
		\vspace{1cm}
		\today\\
		Valentine Chisango (CHSVAL002)\\
		{\tt vmchisango@gmail.com}\\

@@

\begin{abstract}
	\noindent This paper examines numerical methods used to price zero coupon bonds under the Ornstein Uhenbleck process. This paper considers the use of Monte Carlo simulations together with various variance reduction techniques to verify improvments in the stability of estimates. The simulation method is compared to various finitie difference techniques to analyse the difference in convergence and speed in evaluating solutions.The various methods are compared to the closed form solution to assess the accuracy. 
\end{abstract}

@@

\section{Introduction}
\label{sec: Intro}
The pricing of securities is a critical task that many financial institutions must complete. In some instances, these securities have simple enough pricing equations with closed form solutions and so they can be solved analytically. A zero-coupon bond is an example of such an instrument. However, in many cases the closed form solution is not known and a numerical approach is necessary. Most options fall into this category. As such, it is valuable to know which numerical method performs the best and should therefore be used for such cases. Fortunately, the analytical solution for a zero coupon bond can be used to compare the quality of results produced by numerical methods to price the same security and thus draw some conclusions about the performance of these methods for general use.
